Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-11-14 index.qmd
add Laurent's comments

aveiro_plot <-
ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("#70543e", "#CFCFCF"))+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(519749,535233) ,
          ylim=c(4493310,4508794) )+
  ggforce::geom_mark_ellipse(data=Flight_aveiro,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 label.fontsize = 25,
                 label.hjust = 0.5,
                 con.size = 2,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
    # theme_void()+
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
  scale_x_continuous(breaks = seq(-8.70, -8.60, by = 0.10))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))

@@

BB_plot <- ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("#70543e", "#CFCFCF"))+
  geom_sf(data = mask_BB, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(550609,579539) ,
          ylim=c(5189447,5218377) )+
  ggforce::geom_mark_ellipse(data=Flight_BB,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 con.size = 2,
                 label.fontsize = 25,
                 label.hjust = 0.5,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = c(0.95,0.2),
        legend.key.size =  unit(1, "cm"),
        legend.text = element_text(size = 20),
        legend.title=element_blank(),
        legend.background = element_rect(linewidth = 0.5, 
                                         fill = "white",
                                         linetype="solid", 
                                  colour ="black"),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))

@@

Morbihan_plot<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
                    values = c("#70543e", "#CFCFCF"))+
  geom_sf(data = mask_Morb, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(503019,526177) ,
          ylim=c(5257824,5280982))+
  ggforce::geom_mark_ellipse(data=Flight_Morbihan,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 con.size = 2,
                 label.hjust = 0.5,
                 label.fontsize = 25,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  geom_label(aes(x = 505000, y = 5280982-1981, label = "A"), size = 20)+
  scale_x_continuous(breaks = seq(-3, -2.6, by = 0.1))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))

@@

shp_roi<-"Data/reflectance_calibration_low_&_high_flights/" %>%
  list.files(pattern = ".shp", recursive = T, full.names = T) %>%
  read_sf() %>%
  mutate(ID = case_when(name == "Microphytobenthos" ~ 1,
                        name == "ZOS" ~ 2,
                        name == "BL" ~ 3,
                        name == "SED" ~ 4,
                        name == "GRE" ~ 5,
                        name == "RED" ~ 6,
                        name == "Xanthophyceae" ~ 7)) %>% 
  as("Spatial") %>% 
  vect()

@@

p1<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("#70543e", "#BDBDBD"))+
  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+

@@

p1<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("#70543e", "#BDBDBD"))+
  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(519749,535233) ,
          ylim=c(4493310,4508794) )+
  ggforce::geom_mark_ellipse(data=Flight_aveiro,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 label.fontsize = 20,
                 label.hjust = 0.5,
                 con.size = 2,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
    # theme_void()+
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))+
  theme_void()

@@

p1<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("#70543e", "#BDBDBD"))+
  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,show.legend = F,colour="grey30")+
      coord_sf(xlim=c(519749,535233) ,
          ylim=c(4493310,4508794) )+
  ggforce::geom_mark_ellipse(data=Flight_aveiro,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 label.fontsize = 10,
                 label.hjust = 0.5,
                 con.size = 2,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
    # theme_void()+
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))+
  theme_void()
##### ZOOM and masking #####

@@

p1 <- ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
                    values = c("#70543e", "#BDBDBD"))+
  geom_sf(data = mask_BB, mapping = aes(fill = Type), linewidth=0.05,alpha=0.93, show.legend = F,colour="grey30")+
      coord_sf(xlim=c(550609,579539) ,
          ylim=c(5189447,5218377) )+
  ggforce::geom_mark_ellipse(data=Flight_BB,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 con.size = 2,
                 label.fontsize = 10,
                 label.hjust = 0.5,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
  # theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  # geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = c(0.95,0.2),
        legend.key.size =  unit(1, "cm"),
        legend.text = element_text(size = 20),
        legend.title=element_blank(),
        legend.background = element_rect(linewidth = 0.5, 
                                         fill = "white",
                                         linetype="solid", 
                                  colour ="black"),
        # panel.background = element_rect(fill = "#FFFFFF90"),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank())+
  theme_void()

>>>>

aveiro_plot <-
ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("goldenrod", "#CFCFCF"))+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(519749,535233) ,
          ylim=c(4493310,4508794) )+
  ggforce::geom_mark_ellipse(data=Flight_aveiro,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 label.fontsize = 25,
                 label.hjust = 0.5,
                 con.size = 2,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
    # theme_void()+
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
  scale_x_continuous(breaks = seq(-8.70, -8.60, by = 0.10))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))

@@

BB_plot <- ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("goldenrod", "#CFCFCF"))+
  geom_sf(data = mask_BB, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(550609,579539) ,
          ylim=c(5189447,5218377) )+
  ggforce::geom_mark_ellipse(data=Flight_BB,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 con.size = 2,
                 label.fontsize = 25,
                 label.hjust = 0.5,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = c(0.95,0.2),
        legend.key.size =  unit(1, "cm"),
        legend.text = element_text(size = 20),
        legend.title=element_blank(),
        legend.background = element_rect(linewidth = 0.5, 
                                         fill = "white",
                                         linetype="solid", 
                                  colour ="black"),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))

@@

Morbihan_plot<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
                    values = c("goldenrod", "#CFCFCF"))+
  geom_sf(data = mask_Morb, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(503019,526177) ,
          ylim=c(5257824,5280982))+
  ggforce::geom_mark_ellipse(data=Flight_Morbihan,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 con.size = 2,
                 label.hjust = 0.5,
                 label.fontsize = 25,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  geom_label(aes(x = 505000, y = 5280982-1981, label = "A"), size = 20)+
  scale_x_continuous(breaks = seq(-3, -2.6, by = 0.1))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))

@@

# shp_roi<-"Data/reflectance_calibration_low_&_high_flights/" %>%
#   list.files(pattern = ".shp", recursive = T, full.names = T) %>%
#   read_sf() %>%
#   mutate(ID = case_when(name == "Microphytobenthos" ~ 1,
#                         name == "ZOS" ~ 2,
#                         name == "BL" ~ 3,
#                         name == "SED" ~ 4,
#                         name == "GRE" ~ 5,
#                         name == "RED" ~ 6,
#                         name == "Xanthophyceae" ~ 7)) %>% 
#   as("Spatial") %>% 
#   vect()

@@

p1<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("goldenrod", "#BDBDBD"))+
  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+

@@

p1<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("goldenrod", "#BDBDBD"))+
  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),show.legend = F, linewidth=0.05,alpha=0.93,colour="grey30")+
      coord_sf(xlim=c(519749,535233) ,
          ylim=c(4493310,4508794) )+
  ggforce::geom_mark_ellipse(data=Flight_aveiro,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 label.fontsize = 20,
                 label.hjust = 0.5,
                 con.size = 2,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
    # theme_void()+
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))+
  theme_void()

@@

p1<-ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land area"),
                    values = c("goldenrod", "#BDBDBD"))+
  geom_sf(data = p1_background, fill = "white",show.legend = F, linewidth=0.05,alpha=0.93,colour="transparent")+
  geom_sf(data = mask_aveiro, mapping = aes(fill = Type),linewidth=0.05,alpha=0.93,show.legend = F,colour="grey30")+
      coord_sf(xlim=c(519749,535233) ,
          ylim=c(4493310,4508794) )+
  ggforce::geom_mark_ellipse(data=Flight_aveiro,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 label.fontsize = 10,
                 label.hjust = 0.5,
                 con.size = 2,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
    # theme_void()+
  theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  # geom_label(aes(x = 521000, y = 4507794, label = "C"), size = 20)+
  scale_x_continuous(breaks = seq(-8.75, -8.6, by = 0.1))+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))+
  theme_void()
##### ZOOM and masking #####

@@

p1 <- ggplot() +
  scale_fill_manual("", labels = c("Intertidal area", "Land mask"),
                    values = c("goldenrod", "#BDBDBD"))+
  geom_sf(data = mask_BB, mapping = aes(fill = Type), linewidth=0.05,alpha=0.93, show.legend = F,colour="grey30")+
      coord_sf(xlim=c(550609,579539) ,
          ylim=c(5189447,5218377) )+
  ggforce::geom_mark_ellipse(data=Flight_BB,
                 aes(x=lon,
                     y=lat,
                     label = Name,
                     group = Name),
                     # description=Description),
                 size=0.3,
                 fill = "goldenrod",
                 con.colour = "goldenrod4",
                 show.legend=F,
                 con.size = 2,
                 label.fontsize = 10,
                 label.hjust = 0.5,
                 alpha=0.8,
  expand = unit(2, "mm") , 
  radius = unit(2, "mm") ,
  label.fill = "grey90",
  label.buffer = unit(5, "mm")) +
  # theme_Bede_Map()+
  labs(x="Longitude",
       y="Latitude")+
  # geom_label(aes(x = 553460, y = 5216442, label = "B"), size = 20)+
  theme(plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm") ,
        legend.position = c(0.95,0.2),
        legend.key.size =  unit(1, "cm"),
        legend.text = element_text(size = 20),
        legend.title=element_blank(),
        legend.background = element_rect(linewidth = 0.5, 
                                         fill = "white",
                                         linetype="solid", 
                                  colour ="black"),
        # panel.background = element_rect(fill = "#FFFFFF90"),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank())+
  theme_void()
